\documentclass[11pt,a4paper]{moderncv}
\moderncvtheme[blue]{classic}
%\moderncvtheme[black]{banking}

\usepackage[utf8]{inputenc}
\usepackage{textcomp}
\usepackage[top=1.5cm, bottom=1.5cm, left=2cm, right=2cm]{geometry}
 
%\usepackage[french]{babel}     % prend en charge les spécificités du français
 
\usepackage{lmodern}           % charge les polices LatinModern appropriées pour un rendu PDF

\setlength{\hintscolumnwidth}{2.5cm}

\usepackage{xpatch}
\usepackage{setspace}
%\renewcommand{\baselinestretch}{1.5} 
% Add a vertical space before the description
\xpatchcmd\cventry
  {\small}
  {\vspace*{1pt}} % choose what you want
  {}{}

%\vspace*{3ex}
% Increase the vertical spacing between the sections
\makeatletter
\RenewDocumentCommand{\section}{sm}{%
  \par\addvspace{1cm}%
  \phantomsection{}% reset the anchor for hyperrefs
  \addcontentsline{toc}{section}{#2}%
  \parbox[t]{\hintscolumnwidth}{\strut\raggedleft\raisebox{\baseletterheight}{\color{color1}\rule{\hintscolumnwidth}{0.95ex}}}%
  \hspace{\separatorcolumnwidth}%
  \parbox[t]{\maincolumnwidth}{\strut\sectionstyle{#2}}%
  \par\nobreak\addvspace{1ex}\@afterheading}% to avoid a pagebreak after the heading
\makeatother


\usepackage{datenumber,fp}

\newcounter{dateofbirth}
\newcounter{dateoftoday}

\setmydatenumber{dateofbirth}{1992}{10}{15}
\setmydatenumber{dateoftoday}{\the\year}{\the\month}{\the\day}
\FPsub\result{\thedateoftoday}{\thedateofbirth}
\FPdiv\myage{\result}{365.2425}

\firstname{Emmanuel}
\familyname{Payet}
\title{Software Engineer}
\address{International Hall}{Lansdowne Terrace}{WC1N 1AS, London}
\email{contact@emmanuel-payet.me}
\social[github]{epayet}
\mobile{07999 444104}
%\extrainfo{\FPtrunc\myage{\myage}{0}\myage\ ans --- permis b}
%\photo[64pt][0.4pt]{photo}

\begin{document}
\makecvtitle
\vspace*{-7mm}

\section{Personal Statement}
%\cventry{}{}{}{}{}{
%\cvline{}{
    Experimented software engineer specialized in web technologies, looking for a challenging job in London to develop my technical skills. 
%\smallskip
\medskip \newline
    Rigorous and enthusiast programmer who can always be trusted to come up with a new approach. 
    I use as much as possible agile methodologies in my work and personal projects. 
    Productivity is fundamental to me, and I set my toolbox in consequence. 
    I'm capable of handling every step of a project, but I also work well in a team. 
%\smallskip
\medskip \newline
    During my free time, I study new technologies on many subjects (web and mobile technologies, docker, microservices, video game development, raspberry pi, etc.), but my best capacity is my adaptability. 
    All of this makes me someone who tries to find the most effective solutions to computing problems.
%} 

\section{Employment}
\cventry{2013--2015}{Software Engineer - Dual education}{Cdiscount}{Bordeaux, France}{}{
\begin{itemize} \setlength\itemsep{5pt}
    \item Created the developer hub (API documentation and app management) of the Cdiscount openAPI with public access. (\url{http://dev.cdiscount.com})
    \item Developed several internal projects in web technologies (single-page applications, RESTful servers, NoSQL databases). 
    \item Assured the correct implementation of agile methodologies, testing (TDD, integration tests, UI tests, etc.), automation (continuous integration and delivery, docker), and other good development practices (code review, pair programming, constant refactoring, etc.). 
    \item Started migration to microservices. 
    \item Active technological monitoring and organization of knowledge sharing workshops (e.g. coding dojos). 
    \item Trained a junior developer. 
    \item Technologies: OO JavaScript (ES6), AngularJS, NodeJS, MongoDB, Java, Kafka, Docker, Jenkins, git, linux, bower, gulp, karma, jasmine, protractor
\end{itemize}
}
\bigskip

\cventry{2013--3 Months}{Software Engineer - Internship}{Personalized Software Ltd}{Dublin, Ireland}{}{
\begin{itemize} \setlength\itemsep{5pt}
    \item Sonar integration in the continuous integration process (Jenkins) 
    \item Worked on the core architecture of the project BidRight (Java) 
    \item Created a RESTful API (Java / Jersey) 
    \item Created a scraping web app (Python / Django)
\end{itemize}
}

\bigskip

\cventry{2012--2013}{Software Developer - Dual Education}{Cdiscount}{Bordeaux, France}{}{
\begin{itemize} \setlength\itemsep{5pt}
    \item Developed in the web services team on different projects. 
    \item Created an internal application of web service monitoring (SOAP / REST) to ease management and use of web services on different environments (production, dev, etc.), which improved the team productivity. 
    \item Languages: C\#, SQL Server, Silverlight
\end{itemize}
}

\bigskip

\cventry{2012--3 Months}{Web Developer - Internship}{Ecobox}{Bordeaux, France}{}{
\begin{itemize} \setlength\itemsep{5pt}
    \item Developed a Google Map module for Dynmap (cartography software) 
    \item Languages: PHP/MySQL, JavaScript/AJAX
\end{itemize}
}

\section{Education}
\cventry{2010--2015}{EPSI (École Privée des Sciences Informatiques)}{}{}{Bordeaux, France}{
\begin{itemize} \setlength\itemsep{5pt}
    \item Master's degree, Computer Science Engineering Top School  
    \item Relevant Modules: Web, Mobile, NoSQL, SOA, Agile Methodology, Software Architecture, Linux, AI, C/C++, Java, 3D
\end{itemize}
}

\bigskip

\cventry{2007--2010}{Trois Mares High School}{}{}{Reunion Island}{
\begin{itemize} \setlength\itemsep{5pt}
    \item High School diploma (French baccalauréat), Science, Engineering Science, with honours 
    \item French equivalent to A Levels
\end{itemize}
}

\section{Skills}
\cvitem{JavaScript}{ES5 \& ES6, NodeJS, AngularJS, Gulp, Bower, Karma, Jasmine, Protractor, Cordova}
\cvitem{Java}{Version 8, Maven, Gradle, Jersey, JUnit, Hibernate, Groovy, Spock, Kafka}
\cvitem{Database}{MongoDB, ElasticSearch, Redis, PostgreSQL, MySQL}
\cvitem{Operations}{Docker, Jenkins, Heroku, Travis}
\cvitem{Linux}{Debian, ArchLinux, Ubuntu, Fedora}
\cvitem{IDE}{IntelliJ Idea \& derivatives, vim}
\cvitem{Others}{C\#, C/C++, Python, PHP, HTML, CSS, Git}

\section{Languages}
\cvitem{French}{Native}
\cvitem{English}{Full professional proficiency}

\section{Interests}
\cvitem{IT}{New technologies, Coding dojos}
\cvitem{Others}{Video games, Squash, Japanese animation}

\section{References}
Available upon request

%examples
%\cvlanguage{Language 1}{Skill level}{Comment}
%\cvcomputer{category 1}{XXX, YYY, ZZZ}{category 4}{XXX, YYY, ZZZ}
%\cvline{hobby 1}{\small Description}

\end{document}
