\documentclass[11pt,a4paper]{moderncv}
\moderncvtheme[blue]{classic}
%\moderncvtheme[black]{banking}

\input{versions/\jobname}


% stars rate
\usepackage{tikz}
\usetikzlibrary{shapes.geometric,calc}

\newcommand\score[1]{
\pgfmathsetmacro\pgfxa{#1+1}
\tikzstyle{scorestars}=[star, star points=5, star point ratio=2.25, draw,inner sep=0.15em,anchor=outer point 3]
\begin{tikzpicture}[baseline]
  \foreach \i in {1,...,#1} {
    \pgfmathparse{(\i<=#1?"gray":"gray")}
    \edef\starcolor{\pgfmathresult}
    \draw (\i*1em,0) node[name=star\i,scorestars,fill=\starcolor]  {};
  }
  \pgfmathparse{(#1>int(#1)?int(#1+1):0}
  \let\partstar=\pgfmathresult
  \ifnum\partstar>0
    \pgfmathsetmacro\starpart{#1-(int(#1))}
    \path [clip] ($(star\partstar.outer point 3)!(star\partstar.outer point 2)!(star\partstar.outer point 4)$) rectangle 
    ($(star\partstar.outer point 2 |- star\partstar.outer point 1)!\starpart!(star\partstar.outer point 1 -| star\partstar.outer point 5)$);
    \fill (\partstar*1em,0) node[scorestars,fill=yellow]  {};
  \fi

,\end{tikzpicture}
}


\usepackage[utf8]{inputenc}
\usepackage{textcomp}
\usepackage[top=1.5cm, bottom=1.5cm, left=2cm, right=2cm]{geometry}

\usepackage{lastpage}
\rfoot{\addressfont\itshape\textcolor{gray}{Page \thepage\ of \pageref{LastPage}}}
 
%\usepackage[french]{babel}     % prend en charge les spécificités du français
 
\usepackage{lmodern}           % charge les polices LatinModern appropriées pour un rendu PDF

\setlength{\hintscolumnwidth}{2.5cm}

\usepackage{xpatch}

% Add a vertical space before the description
\xpatchcmd\cventry
  {\small}
  {}
%  {\vspace*{1pt}} % choose what you want
  {}{}

% Increase the vertical spacing between the sections
\makeatletter
\RenewDocumentCommand{\section}{sm}{%
  \par\addvspace{0.8cm}%
  \phantomsection{}% reset the anchor for hyperrefs
  \addcontentsline{toc}{section}{#2}%
  \parbox[t]{\hintscolumnwidth}{\strut\raggedleft\raisebox{\baseletterheight}{\color{color1}\rule{\hintscolumnwidth}{0.95ex}}}%
  \hspace{\separatorcolumnwidth}%
  \parbox[t]{\maincolumnwidth}{\strut\sectionstyle{#2}}%
  \par\nobreak\addvspace{1ex}\@afterheading}% to avoid a pagebreak after the heading
\makeatother

% Personal infos
\usepackage{datenumber,fp}

\newcounter{dateofbirth}
\newcounter{dateoftoday}

\setmydatenumber{dateofbirth}{1992}{10}{15}
\setmydatenumber{dateoftoday}{\the\year}{\the\month}{\the\day}
\FPsub\result{\thedateoftoday}{\thedateofbirth}
\FPdiv\myage{\result}{365.2425}

\firstname{Emmanuel}
\familyname{Payet}
\title{Software Engineer}
\address{39 Islington Park Street}{Basement}{N1 1QB, London}
\email{contact@emmanuel-payet.me}
\social[github]{epayet}
% \extrainfo{\FPtrunc\myage{\myage}{0}\myage\ years old}


\begin{document}
\makecvtitle
\vspace*{-14mm}


\section{Personal Statement}
  I am a Software Engineer with 4 years of experience in full-stack development. \newline
  Used to work in a fast-paced agile environment, I build solid web apps on the cloud.
  \medskip \newline
  I define myself as an enthusiast and language agnostic programmer. \newline
  I'm looking for a position in front-end and/or back-end development, where I can expand my knowledge.


\section{Skills}
  \cvitem{\textbf{Agile}}{\score{5} TDD, Continuous delivery, Extreme Programming, SCRUM, Kanban}
  \cvitem{\textbf{JavaScript}}{\score{5} ES5 \& ES6, NodeJS, AngularJS, React, Redux, Webpack, Gulp, Grunt}
  \cvitem{\textbf{Python}}{\score{4}\hspace{1em} Flask, Django}
  \cvitem{\textbf{Tools}}{\score{4}\hspace{1em} Unix shell, Git, IntelliJ Idea \& derivatives, Vim}
  \cvitem{\textbf{CSS}}{\score{4}\hspace{1em} Sass}
  \cvitem{\textbf{Java}}{\score{3}\hspace{2em} Version 8, Maven, Gradle, Jersey, JUnit, Hibernate, Groovy, Spock}
  \cvitem{\textbf{Ops}}{\score{3}\hspace{2em} Docker, CloudFoundry, Heroku, Codeship, Travis, Jenkins}
  \cvitem{\textbf{Database}}{\score{3}\hspace{2em} MongoDB, ElasticSearch, Redis, PostgreSQL, MySQL}
  \cvitem{\textbf{Others}}{\score{2}\hspace{3em} C\#, C/C++, PHP}
  \cvitem{}{\score{1}\hspace{4em} Go, Ruby}


\section{Employment}
  \cventry{Today \\ Nov. 2015 \\ 1 year}{Software Engineer}{Marks \& Spencer}{London, England}{}{
    \begin{itemize} \setlength\itemsep{5pt}
      \item Created CFTO (Christmas Food To Order) website within a medium-size agile team (15 people). \newline
      Twelve-factor app running on mulitple cloud providers allowing us to have a high availability. \newline
      Project developped internally for the first time this year, and is 25\% ahead of last year in revenue. \newline
      Full-stack development: Python (3.5), Flask, Vanilla JavaScript (ES6), HTML, CSS, progressive enhancement, Cloud Foundry, CodeShip, Concourse \newline
      \url{https://christmasfood.marksandspencer.com}
      \item Refactored and added new features to an existing application within a small agile team (4 people). \newline
      Dynamic multistep form to help customers choose their items. Increased conversion. \newline
      Technologies: NodeJS, Angular 1.X, HTML, CSS, Heroku, CodeShip \newline
      \url{https://marksandspencer.com/s/lingerie/be-inspired/bra-fitting-tool}
      \item Started a prototype on the same kind of project but with a more modern web stack: React, Redux, Webpack, Server-side rendering
      \item Started rewriting responsive email templates using open-source tool MJML. \newline
      Uses React components for a better reusability between email templates and more consistency between email providers.
      \item 20\% time: Contributing to various open source projects (MJML + personal) \newline
      Learning new programming languages: Ruby, Go \newline
      Conferences and training: Cloud Foundry, AWS, Ruby
    \end{itemize}
  }

  \bigskip

  \cventry{Jul. 2015 \\ Oct. 2013 \\ 2 years}{Software Engineer}{Cdiscount}{Bordeaux, France}{}{
    \begin{itemize} \setlength\itemsep{5pt}
      \item Created the developer hub of the Cdiscount openAPI, allowing many developers to manage their applications and use the interactive documentation. \newline
      \url{https://dev.cdiscount.com}.
      \item Developed several internal projects using web technologies (single-page applications, RESTful servers, NoSQL databases), which improved the team productivity.
      \item Assured the correct implementation of agile methodologies, testing, automation, and good development practices.
      \item Mentored a junior developer. Organised knowledge sharing workshops (code dojos).
      \item Technologies: OO JavaScript (ES6), AngularJS, NodeJS, MongoDB, Java, Kafka, Docker, Jenkins, Git, Linux, Bower, Gulp, Karma, Jasmine, Protractor
    \end{itemize}
  }

  \bigskip

  \cventry{Sep. 2013 \\ Jul. 2013 \\ 3 months}{Software Engineer Intern}{Personalized Software Ltd}{Dublin, Ireland}{}{
    \begin{itemize} \setlength\itemsep{5pt}
      \item Integration of SonarQube™ in the continuous integration process to improve the overall code quality.
      \item Refactored a part of the core architecture of the project BidRight. Allows users to monitor advertising revenues on different platforms. 
      \item Created a RESTful API around BidRight using the refactored architecture.
      \item Created a scraping app + simple dashboard to check the correct usage of BidRight.
      \item Technologies: Java, Jenkins, Jersey, Python, Django, Mechanize
    \end{itemize}
  }

  \bigskip

  \cventry{Jul. 2013 \\ Sep. 2012 \\ 1 year}{Junior Software Engineer}{Cdiscount}{Bordeaux, France}{}{
    \begin{itemize} \setlength\itemsep{5pt}
      \item Developed in the web services team on different projects. 
      \item Created an internal application of web service monitoring (SOAP / REST) to ease management and use of web services on different environments (production, dev, etc.), which improved the team productivity. 
      \item Technologies: C\#, SQL Server, Silverlight
    \end{itemize}
  }

  \bigskip

  \cventry{Mar. 2012 \\ Jan. 2012 \\ 3 Months}{Web Developer Intern}{Ecobox}{Bordeaux, France}{}{
    \begin{itemize} \setlength\itemsep{5pt}
      \item Developed a Google Map module for Dynmap (cartography software), which combines both software features for users.
      \item Technologies: PHP, MySQL, JavaScript
    \end{itemize}
  }


\section{Education}
  \cventry{2013--2015}{EPSI (École Privée des Sciences Informatiques)}{}{}{Bordeaux, France}{
    \begin{itemize} \setlength\itemsep{5pt}
        \item Master's degree, Computer Science Engineering  
        \item Relevant Modules: Web, Mobile, NoSQL, SOA, Agile Methodology, Software Architecture, Linux, AI, C/C++, Java, 3D
    \end{itemize}
  }

  \bigskip

  \cventry{2010--2013}{EPSI (École Privée des Sciences Informatiques)}{}{}{Bordeaux, France}{
    \begin{itemize} \setlength\itemsep{5pt}
        \item Bachelor's degree, Computer Science Engineering - Web
    \end{itemize}
  }


\section{Languages}
  \cvitem{French}{Native}
  \cvitem{English}{Fluent}


\section{Interests}
  \cvitem{}{Video games, Japanese animation, Squash}


% TODO do I still need this?
% \section{References}
%   \cvitem{}{Available upon request}

% \renewcommand{\listitemsymbol}{} % Changes the symbol used for lists

%   \cvlistdoubleitem{\textbf{Olivier Abrard}}{\textbf{Grégory Taudin}}
%   \cvlistdoubleitem{Engineering Manager}{Engineering Manager}
%   \cvlistdoubleitem{Former Mentor at Cdiscount}{Former Mentor at Cdiscount}
%   \cvlistdoubleitem{\href{mailto:olivier.abrard@gmail.com}{olivier.abrard@gmail.com}}{\href{mailto:gregory.taudin@gmail.com}{gregory.taudin@gmail.com}}
%   \cvlistitem{+33650974994}  %% This will give only one column

%examples
%\cvlanguage{Language 1}{Skill level}{Comment}
%\cvcomputer{category 1}{XXX, YYY, ZZZ}{category 4}{XXX, YYY, ZZZ}
%\cvline{hobby 1}{\small Description}
\end{document}
